Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-03-23 data_appendix.Rmd
Moved mutate statements after select so variable list does not need to be updated every time new variables are added.

```{r import household data}
data_2005 <- read_dta(file.path("Raw data","seminar_paper_data","2005_hhsurvey.dta")) %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        grade = s3_05b,
        repeated = s3_07) %>% 
  mutate(dept = case_when(depto == "1" ~ "Department 1",
                          depto == "2" ~ "Department 2"))

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age, relation, literacy, register, grade, repeated, dept, urb_rur)
```

@@

flood_summary <- flood %>% 
  group_by(dept) %>% 
  summarize_at(vars(starts_with("A_")), sum) %>% 
  pivot_longer(-dept, names_to = "year", names_prefix = "A_", values_to = "floods")

@@

drought_summary %>%
  group_by(dept) %>% 
  summarise(flood = sum(flood))

>>>>

```{r import household data}
data_2005 <- read_dta(file.path("Raw data","seminar_paper_data","2005_hhsurvey.dta")) %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        grade = s3_05b,
        repeated = s3_07)

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, dept0, urb_rur) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```

@@

flood_summary <- flood %>% 
  group_by(dept) %>% 
  summarize_at(vars(starts_with("A_")), sum) %>% 
  pivot_longer(-dept, names_to = "year", names_prefix = "A_", values_to = "floods") %>%
  mutate(year = as.numeric(year))

@@

drought_summary <- drought %>%
  group_by(dept) %>% 
  summarize_at(vars(starts_with("A_")), sum) %>%
  pivot_longer(-dept, names_to = "year", names_prefix = "A_", values_to = "droughts") %>%
  mutate(year = as.numeric(year))
